---
title: "Simulation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,warning=FALSE,message=FALSE}
library(pmkl)
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw())
```

## Introduction

The package **pmkl** is to accompany the publication by Kuwaye and Cho (2024).  Accordingly, it contains both the code used to run the simulations and, since they take a long time, the results produced by the author.  In this vignette, we provide an overview of how the simulations can be reproduced by the inquisitive reader.

## Details

Three clusters, each with their own functional form, were used:
\begin{align*}
  \mu_A(t) &= \log_{10}\left(t+\frac{1}{10}\right) + 1 \\
  \mu_B(t) &= \cos\left(\frac{2\pi}{10}t - \pi\right) + 1 \\
  \mu_C(t) &= -\left(\frac{t-5}{5}\right)^3 + 1 \\
  t&\in[0, 10]
\end{align*}
```{r,echo=FALSE}
data.frame(t = seq(0, 10, length.out = 200)) %>%
  mutate(A = pmkl:::create.A(t),
         B = pmkl:::create.B(t),
         C = pmkl:::create.C(t)) %>%
  pivot_longer(!t, names_to = "oracle", values_to = "f") %>%
  ggplot(aes(x = t, y = f, group = oracle, color = oracle)) +
  geom_line() +
  theme(legend.position = "bottom")
```

We explored the following combinations of measurement schedule (regular, partially random and totally random), number of subjects per group (50:50:50 and 40:50:60), number of observations per subject (50 and 100) and noise level (Normal error with standard deviation of 1, 2 and 3).
```{r}
ss1 <- expand.grid(sigma = 1:3,
                   ni = c(50, 100),
                   Ng = c("50:50:50", "40:50:60"),
                   sp = c("regular", "partially random", "totally random"),
                   KEEP.OUT.ATTRS = FALSE)
ss1$set <- 1:nrow(ss1)
ss1 <- ss1[, ncol(ss1):1]
ss1
```

## Workflow

The simulations were performed with the help of RMarkdown's [parameterized reports](https://bookdown.org/yihui/rmarkdown/parameterized-reports.html).  Using this tool, we iterate over the rows in the previous data frame to provide a set of simulation parameters, which are fed into an RMarkdown file with the corresponding YAML header.  Then the following chunk performs the simulation in parallel for 500 iterations.
```{r,eval=FALSE}
# eval = FALSE
library(doParallel)
n_core <- detectCores() - 1
cl <- makeCluster(n_core)
registerDoParallel(cl)
set.seed(808)
  sim_res <- foreach(sim = 1:500, .combine = rbind) %dopar%
      iteration()
stopCluster(cl)
```

Finally, we have included our raw simulation results, and two functions to calculate summaries and format them to display as mean (sd).
```{r}
data("sim_res")
pmkl:::tab.pii(1)
pmkl:::tab.rival(1)
```
